A quantitative framework for investigating the reliability of empirical network construction

### 2019-02-19 manuscript/reply_to_reviewers_2.tex

\documentclass[12pt]{letter}

\usepackage[britdate]{LiU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\begin{document}

\newpage

\setcounter{page}{1}

% Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly. Changed filtering to reflect all uncertainty, not just detection (more accurate, hopefully less confusing). No box needed, just ``Why sample'' section.

% Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
% To do: expand discussion of our results as much as possible given space constraints.
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

	\begin{refquote}

		Thank you for the extensive and detailed reply to the comments of the referees. Your revised manuscript was sent back to one of the referees who reviewed the original version. As you will see, he is very positive about the revised version and has now signed his review. The only outstanding issue is the addition of some discussion about how to detect potential problems with the priors. I agree with this suggestion as one of the most common criticisms of Bayesian methods is precisely the use of priors.

	\end{refquote}

	\textbf{R:} We appreciate the additional comments from the Referee, and agree that prior detection can be quite a challenge. We are therefore quite happy to add to our discussion about how to detect potential problems. Note, however, that after making the additions requested by the previous round of reviews our manuscript was very close to the standard word limit for \textbf{Methods in Ecology and Evolution}. To meaningfully expand our discussion of how to detect problems with priors we must therefore ask for more space. We have kept our addition to the discussion as succinct as possible, and the revised manuscript is now approximately XXXX words. We hope that this will be an acceptable length for publication in \textbf{Methods in Ecology and Evolution}.

	Thanks again to the Associate Editor and Reviewer for their comments. We believe that the manuscript has been much improved by their feedback.

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1 (Ben Weinstein)}
% ---------------------------------------

	\begin{refquote}

		I am reviewer 1 from the first submission.

		The text is remarkably improved. It is focused and clear. The authors do a good job of identifying the contribution of their work. I appreciate the authors willingness to rewrite much of the paper based on the suggestions of the reviewers.

		I think the authors miss one key discomfort with empirical bayes. It seems vaguely anti-ecology, because it assumes that we can L289 : “use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.”  A common goal in network ecology is to describe interaction frequencies by using niche-based proxies (phylogeny, traits, etc). If it was a simply a matter that most networks had the same degree distribution, then predicting networks would be much easier than it is. In fact, we are really bad at predicting pairwise interactions (see Olito and Fox), even when we get the emergent structure of the network correct. Yet empirical bayes assumes a kind of commonality among all networks to help narrow the posteriors. I think the authors need to speak to this concern.

		Sincerely,

		Ben Weinstein

	\end{refquote}

	We thank the Reviewer for his further feedback and address each point (prefaced by \textbf{R:}) below.

	1. Re-emphasize Figure 3.

		\begin{refquote}

			Figure 3 is fun and deserves a bit more central place in the discussion.

		\end{refquote}

		\textbf{R:} We thank the Reviewer for his complement to Figure 3. Although we wish to keep any additions as brief as possible, we are happy to add a short reference to Figure 3 in the discussion as part of an example of how to use our simple Bayesian framework when thinking about insects moving into new communities (e.g., as climate changes). We hope that this puts the figure in a more central place, as intended. We also now compare this reasonable posterior pdf with an un-reasonable one generated by a poor choice of prior, which should further highlight this figure.

		Lines XX-XX:

		\begin{quotation}

			Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Our framework could, for example, be used to predict the probability of interaction between a galler and parasitoid at a new site on the frontier of their ranges. If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig.~\ref{Salix_pdfs_cdfs}). Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

		\end{quotation}

	2.

	3. Include material from \emph{Appendix 7} in the main text

		\begin{refquote}

			My final lingering concern is that something like appendix 7 seems important and should be included in the text? Was this done because of space limitations? I think the authors can appeal to the editor that the paper merits the extra space. As a compromise there could to be atleast a paragraph on what can go wrong and what that looks like. I think a figure would be useful here. If the informed/empirical priors are too narrow, the data will not really move the posterior. The authors certainly acknowledge it in various places, but it needs to be clearer to the reader.

		\end{refquote}

		\textbf{R:} This material was indeed placed in an appendix because of space constraints. We have added a figure showing results with the other prior and a paragraph summarizing \emph{Appendix 7}. As we do not wish to be too demanding with regard to extra space (and our manuscript was essentially at the standard length limit after the last revision), we hope that these smaller additions will be enough to emphasize the potential for spurious results after poor prior choices.

	3. Reduce citations by Graham and Weinstein

		\begin{refquote}

			To be perfectly honest, I feel more than a bit uncomfortable with the amount that Graham and Weinstein are cited in the introduction. I count 18 times. It would be more than sufficient to cite the work in the appropriate places and move on. I understand that the reviewers asked for a broader sense of the literature, but I think the authors have gone a bit overboard. I don’t know how often a reviewer asks the authors to cite himself less, but I assure you the reason that the paper is improved is not because I am cited nearly twenty times.

		\end{refquote}

\clearpage

    \bibliographystyle{ecol_let} 
    \bibliography{manual} % Abbreviate journal titles.

\end{document}

### 2019-02-19 manuscript/reply_to_reviewers_2.tex

		\begin{refquote}

			Figure 3 is fun and deserves a bit more central place in the discussion.

		\end{refquote}

		\textbf{R:} We thank the Reviewer for his complement to Figure 3. Although we wish to keep any additions as brief as possible, we are happy to add a short reference to Figure 3 in the discussion as part of an example of how to use our simple Bayesian framework when thinking about insects moving into new communities (e.g., as climate changes). We hope that this puts the figure in a more central place, as intended. We also now include a similar figure demonstrating the effect of a change in prior on the posterior pdf's obtained for the \emph{Salix}-galler networks and hope that this also helps to emphasize these results.

@@

			Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Our framework could, for example, be used to predict the probability of interaction between a galler and parasitoid at a new site on the frontier of their ranges. If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig.~\ref{Salix_pdfs_cdfs}). Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

		\end{quotation}

	2.

		\textbf{R:} We agree that pairwise interactions are often difficult to predict and that different networks can have quite different degree distributions (or whichever other network property you like).  We disagree, however, that empirical Bayes assumes commonality among all networks. Rather, we argue that given some \emph{a priori} similarity among networks (e.g., similar taxa, similar habitats, similar interaction types, similar numbers of species, etc.), we can use that similarity to set bounds on our expectations about pairwise interactions. Including clearly dissimilar networks in the set of networks used to create an empirical Bayesian prior would not be reasonable. We do point out some of the potential for false results due to the use of very different networks for the prior and posterior in our paragraph on degree distribution, and have added a few more references to the pitfalls of empirical Bayes.

		We would also like to add that we began our discussion of informed priors with trait-based models because these models are likely to give the best results in terms of which specific interactions are most likely. We introduce empirical Bayes for those situations where researchers do not have a strong idea of the "niche-based proxies" structuring interactions in a given site. In such a situation, we still maintain that using information available from well-sampled species or other networks is likely to be better than nothing. For example, we know that empirical networks in general tend to be rather sparse and the well-sampled species in a community probably do not interact will all possible partners, so it is not reasonable to assume that every unobserved interaction truly occurs (leaving a completely connected network) except in extremely unusual circumstances. Granted, this is quite an extreme example, but it illustrates the point.

		The Reviewer is quite correct that an empirical Bayes framework does not tell us which interactions are most likely to truly occur (assuming equal observations of co-occurrences). While there are many studies which aim to identify the exact set of interactions which occur, there are also others that are more concerned with the structure of the network as a whole. In such cases, and absent the information necessary to build a more specific model, we feel that empirical Bayes can still be a useful tool. We hope that our additions to this section will now instill an appropriate level of caution in readers without making it seem as though empirical Bayes is completely useless. After all, we do have some faith in our empirical Bayes example.

	3. Include material from \emph{Appendix 7} in the main text [[done]]

@@

		\begin{refquote}

			My final lingering concern is that something like appendix 7 seems important and should be included in the text? Was this done because of space limitations? I think the authors can appeal to the editor that the paper merits the extra space. As a compromise there could to be atleast a paragraph on what can go wrong and what that looks like. I think a figure would be useful here. If the informed/empirical priors are too narrow, the data will not really move the posterior. The authors certainly acknowledge it in various places, but it needs to be clearer to the reader.

		\end{refquote}

		\textbf{R:} This material was indeed placed in an appendix because of space constraints. We have added a figure showing the posterior distributions obtained from both priors and a paragraph summarizing \emph{Appendix 7}. As we do not wish to be too demanding with regard to extra space (and our manuscript was essentially at the standard length limit after the last revision), we hope that these smaller additions will be enough to emphasize the potential for spurious results after poor prior choices. Also note that the results for the galler-parasitoid community were somewhat similar. In order to more clearly demonstrate the potentially large effects of prior choice, we therefore showcase the results from \emph{Salix}-galler networks in this paragraph.

		  Note that, as in all Bayesian analyses, our results do depend on the prior chosen. To demonstrate this, we repeated our analyses using a prior derived from a study of gallers found on several genotypes of \emph{Salix hookeriana} and the parasites which emerged from them (\citealp{Barbour2016,Barbour2016Dryad}; \emph{Appendix S7}). Although the study system is similar to that in~\citet{Kopelke2017}, the network is quite different due to using different genotypes of a single \emph{Salix} species rather than several \emph{Salix} species as the basis for sampling. While this had a relatively small effect on our expectations for the galler-parasitoid community (\emph{Appendix S7}), the prior based on \citep{Barbour2016} resulted in very high probabilities of interaction between \emph{Salix} and galler pairs that were not observed interacting (Fig.~\ref{prior_comparison}). No amount of additional sampling would allow us to conclude that a given \emph{Salix}-galler pair did not interact with a threshold interaction probability of 0.01. This is reasonable for the situation described in~\citet{Barbour2016}, as it is very likely that gallers which can interact with one \emph{S. hookeriana} genotype can interact with most others, but is not reasonable for the more diverse community in~\citet{Kopelke2017}. This demonstrates the importance of conducting a "sanity check" on the posterior distribution obtained from any given prior.

	3. Reduce citations by Graham and Weinstein [[done]]

@@

		\begin{refquote}

			To be perfectly honest, I feel more than a bit uncomfortable with the amount that Graham and Weinstein are cited in the introduction. I count 18 times. It would be more than sufficient to cite the work in the appropriate places and move on. I understand that the reviewers asked for a broader sense of the literature, but I think the authors have gone a bit overboard. I don’t know how often a reviewer asks the authors to cite himself less, but I assure you the reason that the paper is improved is not because I am cited nearly twenty times.

		\end{refquote}

		\textbf{R:} We have removed several of the citations to Graham and Weinstein/Weinstein and Graham, and thank the Reviewer for the opportunity to reduce our word count slightly. We had added particularly many citations of these papers because a couple of the Reviewers mentioned Graham and Weinstein as references that we had missed, and so we hope that the reduced number of references in the present revision still does justice to your work.

### 2019-02-19 manuscript/CI_interactions.tex
removed some Weinstein and Graham refs

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2018,Graham2018}. Even assuming constant co-occurrence within a system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers note effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}). Assessments of the accumulation of interactions with increasing sampling effort suggest that it is more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Such efforts usually take the form of creating model networks that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Model networks provide an important ''reality check'' by allowing hypothesis testing about factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}. They can also allow estimation of the numbers unobserved of interactions~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2018}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system. Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes rarely-observed species.

@@

    In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of interaction probabilities. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network data we could find has substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. 
    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Pelissier2017,Tylianakis2017,Weinstein2017}.

    % Development of molecular sampling methods such as DNA barcoding hold great potential for uncovering interactions missed by other sampling methods (such as visit surveys)~\citep{Giron2018}, but these novel methods are also somewhat error-prone at present~\citep{}.

    % Accounting for differences in feasible (binary) interactions across life stages changes network structure~\citep{Clegg2018}.

    % Representing an ecological community as a network summarises both species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    % The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Worse, variability in community composition and interactions may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015} or individual preferences~\citep{Fodrie2015}.

    % Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012,Bartomeus,others}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    % Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling. [[cite previous attempts]] Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

    % In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths. To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.

@@

          A feasible interaction (i.e., $L_{ij}=1$;), still may not occur at a particular place and time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs, an interaction may not occur locally because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij}=1)=\chi_{ij}$. It is unlikely that $\chi_{ij}=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi_{ij}<1$, we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies. Phenological matching~\citep{MillerRushing2010}, species preferences~\citep{Pires2011a,Novak2015}, and fear effects~\citep{Luttbeg2005} all affect the probability of an interaction and could be included in models similar to trait-matching models. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. This approach does reduce local-scale uncertainty but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of micro-habitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample extensively in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.

@@

        We often have some prior knowledge which can inform uncertainty about interactions. One common example is the well-justified assumption that plants never consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,Graham2018,Gravel2018}. Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

        Using an informative prior tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models). Despite these benefits, informative priors often involve many assumptions and carry a risk of over-fitting. Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks~\citep{Jordano2016}. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a,Weinstein2017}.

@@

@@

>>>>

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2018,Graham2018}. Even assuming constant co-occurrence within a system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers note effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}). Assessments of the accumulation of interactions with increasing sampling effort suggest that it is more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Such efforts usually take the form of creating model networks that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Model networks provide an important ''reality check'' by allowing hypothesis testing about factors structuring ecological networks~\citep{Bartomeus2013,Graham2018}. They can also allow estimation of the numbers unobserved of interactions~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2018}) or very system-specific (e.g.,~\citet{Bartomeus2013,Graham2018}); in either case such a model may be a poor fit for a particular study system. Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes rarely-observed species.

@@

    In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of interaction probabilities. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network data we could find has substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.

@@

          A feasible interaction (i.e., $L_{ij}=1$;), still may not occur at a particular place and time~\citep{Poisot2015}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs, an interaction may not occur locally because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij}=1)=\chi_{ij}$. It is unlikely that $\chi_{ij}=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi_{ij}<1$, we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies. Phenological matching~\citep{MillerRushing2010}, species preferences~\citep{Pires2011a,Novak2015}, and fear effects~\citep{Luttbeg2005} all affect the probability of an interaction and could be included in models similar to trait-matching models. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017a}. This approach does reduce local-scale uncertainty but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of micro-habitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample extensively in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.

@@

        We often have some prior knowledge which can inform uncertainty about interactions. One common example is the well-justified assumption that plants never consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,s,Gravel2018}. Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

        Using an informative prior tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models). Despite these benefits, informative priors often involve many assumptions and carry a risk of over-fitting. Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017a}).

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks~\citep{Jordano2016}. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a}.

@@

  Note that, as in all Bayesian analyses, our results do depend on the prior chosen. To demonstrate this, we repeated our analyses using a prior derived from a study of gallers found on several genotypes of \emph{Salix hookeriana} and the parasites which emerged from them (\citealp{Barbour2016,Barbour2016Dryad}; \emph{Appendix S7}). Although the study system is similar to that in~\citet{Kopelke2017}, the network is quite different due to using different genotypes of a single \emph{Salix} species rather than several \emph{Salix} species as the basis for sampling. While this had a relatively small effect on our expectations for the galler-parasitoid community (\emph{Appendix S7}), the prior based on \citep{Barbour2016} resulted in very high probabilities of interaction between \emph{Salix} and galler pairs that were not observed interacting (Fig.~\ref{prior_comparison}). No amount of additional sampling would allow us to conclude that a given \emph{Salix}-galler pair did not interact with a threshold interaction probability of 0.01. This is reasonable for the situation described in~\citet{Barbour2016}, as it is very likely that gallers which can interact with one \emph{S. hookeriana} genotype can interact with most others, but is not reasonable for the more diverse community in~\citet{Kopelke2017}. This demonstrates the importance of conducting a "sanity check" on the posterior distribution obtained from any given prior.

@@

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), A) based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} and B) based on a network describing interactions between gallers and several genotypes of \emph{Salix hookeriana} from~\citet{Barbour2016}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. Note that the prior obtained from~\citet{Barbour2016} constrains the MLE  of $\lambda_{ij}$ above 0.01.}
    \label{prior_comparison}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/SG_pdfs_prior_comparison.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
    \end{center}
    \end{figure}
